%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{hyperref}

% DOCUMENT LAYOUT
\usepackage[margin=1.2in]{geometry} 
\setlength\parindent{0in}

% fix for pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Reduce spacing in itemize, enumerate and titles
\usepackage{multicol}
\usepackage{enumitem}
\setenumerate{nolistsep}
\setitemize{nolistsep}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (quotes'' --- dashes etc.) to unicode
% \setromanfont[Ligatures={Common}, Numbers={OldStyle}]{Palatino}
% \setmonofont[Scale=1.0]{Monaco} 
% \setsansfont[Scale=1.0]{Optima Regular} 

% HEADINGS and TITLES
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\sffamily\mdseries\large\underline} % Underlines headings
\setcounter{secnumdepth}{-1} % Removes the numbers before sections
\subsectionfont{\rmfamily\mdseries\scshape\normalsize}
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}

\usepackage{titling}
\setlength{\droptitle}{-90pt} % The negative number moves the title closer to the top of the page
\title{Curriculum Vitae} % name Curriculum Vitae
\date{13 September 2018\\} % Leave blank to remove the date
\author{Henrik Nicolay Topnes Finsberg\\\\
  http://henrikfinsberg.com\\\\
Jongsbruveien 27B \textbar{} Sandvika, 1338\\ %Put your address here
+47 911 868 43 \textbar{} henriknf@simula.no } % put your contact information here

% BEGIN DOCUMENT
\begin{document}
\maketitle
\begin{raggedright}
\href{latex/cv.pdf}{PDF}

\hypertarget{personal-summary}{%
\subsubsection{Personal summary}\label{personal-summary}}

\begin{quote}
In October 2017 I started as a Research Engineer at Simula Research
Laboratory in the department for Scientific Computing, and will work
with development of computational modeling tools primarily with
application in electrophysiology.
\end{quote}

\begin{quote}
Before I started as a Research Engineer I was a PhD student in the
Cardiac Modelling group in the department for Scientific Computing, also
at Simula Research Laboratory. In my PhD I worked with patient specific
models of the cardiac mechanics, and defended it at January 17th 2018.
\end{quote}

\begin{quote}
I graduated in 2014 after finishing a joint master degree in Applied and
Engineering Mathematics at NTNU in Trondheim and DTU in Copenhagen. My
fields of interests are mathematical modelling, geometric modelling and
image processing. In my master thesis I studied methods for image
classification of ultrasound images based on convolutional neural
networks.
\end{quote}

\hypertarget{education}{%
\subsubsection{Education}\label{education}}

\begin{itemize}
\tightlist
\item
  2014 - 2017: PhD Scientific Computing, Simula Research Laboratory and
  University of Oslo, Oslo (Norway)
\end{itemize}

\begin{quote}
Title: Patient-specfic computational modeling of cardiac mechanics.
\end{quote}

\begin{itemize}
\tightlist
\item
  2012 - 2014: MSc. Applied and Engineering Mathematics, Nordic Master
  in Applied and engineering mathematics(N5TeAM), Trondheim (Norway),
  Copenhagen (Denmark)
\end{itemize}

\begin{quote}
Joint master program with first year at DTU in Copenhagen, and second
year at NTNU in Trondheimm. Degree from NTNU Trondheim: Master of
Science in Applied and Engineering Mathematics. Degree DTU Copenhagen:
Master of Science in Engineering. Master thesis title: Wavelet
Techniques in Medical Imaging. Final Grade A (Best: A Average: A Worst:
C)
\end{quote}

\begin{quote}
\href{/assets/cv/transcripts_NTNU.pdf}{Transcript NTNU}
\end{quote}

\begin{quote}
\href{/assets/cv/transcripts_DTU.pdf}{Transcript DTU}
\end{quote}

\begin{itemize}
\tightlist
\item
  2010 -- 2012 MSc. Physics and Mathematics, NTNU, Trondheim (Norway).
\end{itemize}

\begin{quote}
Specialized in industrial mathematics. Switched to
\href{http://n5team.aalto.fi/en/}{N5TeAM} after finishing first year at
industrial mathematics.
\end{quote}

\begin{itemize}
\tightlist
\item
  2006 -- 2008: Sergeant, Army Officer Candidate School, Skjold
  (Norway).
\end{itemize}

\begin{quote}
Two-year officer school in the engineering battalion. Final Grade C
(Best: A Average: B Worst: C)
\end{quote}

\hypertarget{technical}{%
\subsubsection{Technical}\label{technical}}

\begin{itemize}
\tightlist
\item
  Expert: \href{https://www.python.org}{Python},
  \href{https://en.wikipedia.org/wiki/Unix}{Unix},
  \href{https://www.latex-project.org}{LaTeX},
  \href{https://fenicsproject.org}{FEniCS},
  \href{https://en.wikipedia.org/wiki/Linux}{Linux},
\item
  Intermediate: \href{https://www.docker.com}{Docker}
  \href{https://en.wikipedia.org/wiki/HTML}{HTML},
  \href{https://en.wikipedia.org/wiki/Bash_(Unix_shell)}{Bash},
  \href{https://se.mathworks.com/products/matlab.html}{Matlab},
  \href{https://git-scm.com}{Git}, \href{http://jupyter.org}{Jupyter},
  \href{https://www.vtk.org}{VTK}, \href{http://gmsh.info}{Gmsh},
  \href{https://www.paraview.org}{Paraview}
\item
  Basic:
  \href{https://en.wikipedia.org/wiki/Cascading_Style_Sheets}{CSS},
  \href{https://en.wikipedia.org/wiki/JavaScript}{JavaScript},
  \href{https://en.wikipedia.org/wiki/C\%2B\%2B}{C++},
  \href{https://en.wikipedia.org/wiki/C_(programming_language)}{C},
  \href{https://en.wikipedia.org/wiki/C_Sharp_(programming_language)}{C\#},
  \href{https://kubernetes.io}{Kubernetes},
  \href{https://www.r-project.org/about.html}{R},
  \href{http://www.swig.org}{Swig}
\end{itemize}

\hypertarget{employment}{%
\subsubsection{Employment}\label{employment}}

\begin{itemize}
\tightlist
\item
  2017-present: Research Engineer, \href{https://www.simula.no}{Simula
  Research Laboratory}
\end{itemize}

\begin{quote}
Development of high performace copmuitational software tools and
mathematical models for the study of Human Induced Pluripotent Stem
Cells (hiPSC)
\end{quote}

\begin{itemize}
\tightlist
\item
  2016: Corrector, University of Oslo
\end{itemize}

\begin{quote}
Correcting assignments for master students in the course {[}INF4331,
Problem solving with high level languanges{]}
(https://www.uio.no/studier/emner/matnat/ifi/INF4331/index-eng.html)
\end{quote}

\begin{itemize}
\tightlist
\item
  2009 -- 2013 Teaching Assistant, Norwegian University of Science and
  Technology, Trondheim.
\end{itemize}

\begin{quote}
Assisted groups of 25 students in Calculus 1, Calculus 2, Calculus 3,
Statistics and Information Technology.
\end{quote}

\begin{itemize}
\tightlist
\item
  2012 -- 2012 Summer Intern, \href{https://www.silabs.com}{Energy
  Micro}, Oslo, Norway.
\end{itemize}

\begin{quote}
Porting the Energy Micro University program to Giant Gecko Starter Kit.
Improving code and embedded documentation as well as look and usability
of the doxygen generated documentation for all kits.
\end{quote}

\begin{itemize}
\tightlist
\item
  2011 -- 2012 Mentor, \href{https://www.ent3r.no}{ENT3R} NTNU,
  Trondheim.
\end{itemize}

\begin{quote}
Responsibility for a class of 20 students from high school. Help
students with mathematics, and motivate them for further education in
science.
\end{quote}

\begin{itemize}
\tightlist
\item
  2011 -- 2011 Summer Intern, \href{https://www.ffi.no}{Norwegian
  Defence Research Establishment (FFI)}, Kjeller.
\end{itemize}

\begin{quote}
Created a GUI in Visual C\# and Matlab to read the log files, and use
this information to calculate and plot the desired data.
\end{quote}

\begin{itemize}
\tightlist
\item
  2007 - 2008: Squad leader, Engineering Batalion, Norwegian Army
\end{itemize}

\begin{quote}
Responsibilities: Educate soldiers with background in construction, and
lead small construction projects.
\end{quote}

\hypertarget{activities}{%
\subsubsection{Activities}\label{activities}}

\begin{itemize}
\tightlist
\item
  2015-2016 Member of Excepert Committee, Nokut, Oslo.
\end{itemize}

\begin{quote}
Responsible for evaluating an application for accreditation of a PhD
program at Bergen university college together with three other experts.
\href{https://www.nokut.no/contentassets/8709159cefe84f72b68ea2f251f6130a/computer_science_software_engineering_sensor_networks_and_engineering_computing_phd_hib_2016.pdf}{Report}
\end{quote}

\begin{itemize}
\tightlist
\item
  2011-2012 Business Manager, ENT3R NTNU, Trondheim.
\end{itemize}

\begin{quote}
Responsible for organizing student events and invite companies to these
events.
\end{quote}

\begin{itemize}
\tightlist
\item
  2011-2012 Chairman for the Business Committee, Nabla - Applied Physics
  and Mathematics student association , Trondheim.
\end{itemize}

\begin{quote}
Overall responsibility for hosting business presentations, publishing
catalogue with summer jobs, and connect students to the industry.
\end{quote}

\begin{itemize}
\tightlist
\item
  2011-2012 Member of the Business Committee, Nabla - Applied Physics
  and Mathematics student association , Trondheim.
\end{itemize}

\begin{quote}
Responsible for contacting 20 companies and arrange business
presentations.
\end{quote}

\hypertarget{scholarships-and-awards}{%
\subsubsection{Scholarships and Awards}\label{scholarships-and-awards}}

\begin{itemize}
\tightlist
\item
  Abel Scholarship 2012
\end{itemize}

\begin{quote}
Given to mathematics students that exchange abroad.
\end{quote}

\begin{itemize}
\tightlist
\item
  Fullbright Scholarship
\end{itemize}

\begin{quote}
My initial plan was to exchange to US and therefore I also applied for
the Fullbright scholarship. I was awarded this scholarship but had to
decline when I decided that I wanted to go to Denmark instead.
\end{quote}

\begin{itemize}
\tightlist
\item
  Norplus scholarship
\end{itemize}

\begin{quote}
Given to exchange students in the nordic countries.
\end{quote}

\begin{itemize}
\tightlist
\item
  Erasmus scholarship
\end{itemize}

\begin{quote}
Given to exchange students in Europe.
\end{quote}

\hypertarget{thesis}{%
\subsubsection{Thesis}\label{thesis}}

\begin{itemize}
\item
  Finsberg, H.N., 2017. Patient-Specific Computational Modeling of
  Cardiac Mechanics. Series of dissertations submitted to the Faculty of
  Mathematics and Natural Sciences, University of Oslo.
  \href{https://www.duo.uio.no/bitstream/handle/10852/62015/PhD-Finsberg-2018.pdf}{PDF}
\item
  Finsberg, H.N., 2014. Wavelet Techniques in Medical Imaging:
  Classification of UltraSound Images using the Windowed Scattering
  Transform (Master's thesis, Institutt for matematiske fag).
  \href{https://brage.bibsys.no/xmlui/bitstream/handle/11250/259333/733307_FULLTEXT01.pdf}{PDF}
\end{itemize}

\hypertarget{publications}{%
\subsubsection{Publications}\label{publications}}

\begin{itemize}
\item
  Balaban, G., Finsberg, H., Funke, S., Håland, T.F., Hopp, E., Sundnes,
  J., Wall, S. and Rognes, M.E., 2018. In vivo estimation of elastic
  heterogeneity in an infarcted human heart. Biomechanics and modeling
  in mechanobiology, pp.1-13.
  \href{https://doi.org/10.1007/s10237-018-1028-5}{DOI}
  \href{https://link.springer.com/content/pdf/10.1007\%2Fs10237-018-1028-5.pdf}{PDF}
\item
  Finsberg, H., Xi, C., Tan, J.L., Zhong, L., Genet, M., Sundnes, J.,
  Lee, L.C. and Wall, S.T., 2018. Efficient estimation of personalized
  biventricular mechanical function employing gradient‐based
  optimization. International journal for numerical methods in
  biomedical engineering, p.e2982.
  \href{https://doi.org/10.1002/cnm.2982}{DOI}
  \href{https://onlinelibrary.wiley.com/doi/pdf/10.1002/cnm.2982}{PDF}
  \href{https://bitbucket.org/finsberg/efficient-estimation-of-personalized-biventricular-mechanical}{CODE}
\item
  Finsberg, H., Balaban, G., Ross, S., Håland, T.F., Odland, H.H.,
  Sundnes, J. and Wall, S., 2018. Estimating cardiac contraction through
  high resolution data assimilation of a personalized mechanical model.
  Journal of computational science, 24, pp.85-90.
  \href{https://doi.org/10.1016/j.jocs.2017.07.013}{DOI}
  \href{https://www.sciencedirect.com/science/article/pii/S1877750317308190/pdfft?md5=3f7bbc82a870dc84f5080564c7f3c33a\&pid=1-s2.0-S1877750317308190-main.pdf}{PDF}
  \href{https://bitbucket.org/finsberg/estimate_cardiac_contraction}{CODE}
\item
  Balaban, G., Finsberg, H., Odland, H.H., Rognes, M.E., Ross, S.,
  Sundnes, J. and Wall, S., 2017. High‐resolution data assimilation of
  cardiac mechanics applied to a dyssynchronous ventricle. International
  journal for numerical methods in biomedical engineering, 33(11),
  p.e2863. \href{https://doi.org/10.1002/cnm.2863}{DOI}
  \href{https://www.duo.uio.no/bitstream/handle/10852/62016/Balaban_et_al-2017-cnm-2863.pdf}{PDF}
  \href{https://bitbucket.org/finsberg/cardiac_highres_dataassim}{CODE}
\end{itemize}

\hypertarget{conference-proceedings-and-preprints}{%
\subsubsection{Conference proceedings and
preprints}\label{conference-proceedings-and-preprints}}

\begin{itemize}
\item
  Finsberg, H., Balaban, G., Rognes, M.E., Sundnes, J. and Wall, S.,
  Patient-specific computational modeling of cardiac biomechanics via
  gradient based data assimilation, 8th World Congress of Biomechanics,
  Dublin, Ireland,
  \href{https://www.researchgate.net/publication/328733786_Patient-specific_computational_modeling_of_cardiac_biomechanics_via_gradient_based_data_assimilation}{PDF}
\item
  Finsberg, H., Aalen, J., Larsen, C. J., Remme E., Sundnes, J. Smiseth
  O. A, and Wall, S., Assessment of regional myocardial work through
  adjoint-based data assimilation, International Conference on
  Computational Science and Engineering, Oslo, Norway
  \href{https://www.researchgate.net/publication/328733792_Assessment_of_regional_myocardial_work_through_adjoint-based_data_assimilation}{PDF}
\item
  Finsberg, H., Xi, C., Tan, J.L., Zhong, L., Sundnes, J., Lee, L.C. and
  Wall, S.T.,, Mechanical Analysis of Pulmonary Hypertension via Adjoint
  based data assimilation of a Finite Element model, SB3C2017 Summer
  Biomechanics, Bioengineering and Biotransport ConferenceAt: Tucson,
  AZ, USA
  \href{https://www.researchgate.net/publication/325301179_MECHANICAL_ANALYSIS_OF_PULMONARY_HYPERTENSION_VIA_ADJOINT_BASED_DATA_ASSIMILATION_OF_A_FINITE_ELEMENT_MODEL}{PDF}
\item
  Finsberg, H., Balaban, G., Ross, S., Odland, H.H., Sundnes, J. and
  Wall, S., Personalized Cardiac Mechanical Model using a High
  Resolution Contraction Field, Virtual Physiological Human 2016
  conference, Amsterdam, Netherland
  \href{https://www.researchgate.net/publication/328733694_Personalized_Cardiac_Mechanical_Model_using_a_High_Resolution_Contraction_Field}{PDF}
\item
  Finsberg, H., Balaban, G., Ross, S., Odland, H.H., Sundnes, J. and
  Wall, S., Personalization of a Cardiac Computational Model using
  Clinical Measurements, 28th Nordic Seminar on Computational Mechanics,
  Tallinn, Estonia
  \href{https://www.researchgate.net/publication/325301428_Personalization_of_a_Cardiac_Computational_Model_using_Clinical_Measurements}{PDF}
\item
  Finsberg, H., Luybarskii, Y., Growth of entire functions via Borel
  transform, TMA4500 Specialization project, 2013
  \href{http://doi.org/10.13140/RG.2.2.10460.44160}{DOI}
  \href{https://www.researchgate.net/profile/Henrik_Finsberg/publication/327633791_Growth_of_entire_functions_via_Borel_transform/links/5b9ab94145851574f7c5a499/Growth-of-entire-functions-via-Borel-transform.pdf}{PDF}
\end{itemize}

\hypertarget{posters}{%
\subsubsection{Posters}\label{posters}}

\begin{itemize}
\item
  Geilo Winter School: Scientific Visualization, 2016
  \href{/assets/posters/geilo_winter_school_2016.pdf}{PDF}
\item
  Summer Biomechanics, Bioengineering, and Biotransport Conference
  (SB3C), Tucson, AZ 2017 \href{/assets/posters/sb3c_2017.pdf}{PDF}
\item
  The Heart by Numbers: Integrating Theory, Computation and Experiment
  to Advance Cardiology, Berlin 2018
  \href{/assets/posters/heart_by_numbers_2018.pdf}{PDF}
\end{itemize}

\hypertarget{phd-defence}{%
\subsubsection{PhD Defence}\label{phd-defence}}

\begin{itemize}
\item
  PhD defence, Patient-Specific Computational Modeling of Cardiac
  Mechanics 17.01.18, Oslo, Norway \href{/assets/talks/defence.pdf}{PDF}
\item
  PhD trial lecture, How do the mechanics and structure of the heart
  matter in regard to patient-specific cardiac modelling? 17.01.18,
  Oslo, Norway \href{/assets/talks/trial_lecture.pdf}{PDF}
\end{itemize}

\hypertarget{conference-talks}{%
\subsubsection{Conference talks}\label{conference-talks}}

\begin{itemize}
\item
  Assessment of regional myocardial work through adjoint-­based data
  assimilation, International Conference on Computational Science and
  Engineering 2017, Oslo Norway, \emph{In memory of Hans Petter
  Langtangen} \href{/assets/talks/CSE251017.pdf}{PDF}
\item
  Optimization of a Spatially Varying Cardiac Contraction parameter
  using the Adjoint Method, FEniCS Conference 2016, Oslo, Norway,
  \href{/assets/talks/fenics2016.pdf}{PDF}
\item
  What are all these models, and do we really need them? - Translating
  cardiac mechanical modeling into clinical applications, CCI Journal
  Club, Oslo University Hospital
  \href{/assets/talks/journal_club270317.pdf}{PDF}
\item
  Patient Constrained Ventricular Stress Mapping, MALT Conference,
  Lugano, Switzerland, 2015, \href{/assets/talks/malt010515.pdf}{PDF}
\item
  Personalization of a Cardiac Computational Model using Clinical
  Measurements, 28th Nordic Seminar on Computational Mechanics, Tallin,
  Estonia, 2015, \href{/assets/talks/nscm_2015.pdf}{PDF}
\end{itemize}

\hypertarget{references}{%
\subsubsection{References}\label{references}}

Available on request.
\end{raggedright}
\end{document}
